## Einzelteile einlesen
#1
```{r, message=FALSE, warning = FALSE, cache = TRUE}
txt <- readLines("Data/Einzelteil/Einzelteil/Einzelteil_T01.txt")
txt <- gsub(" | | ",",",txt, fixed = TRUE)
txt <- gsub(" ","\n",txt, fixed = TRUE)
part_T01 <- fread(text = txt, sep = ",", data.table = FALSE) %>% 
  filter((Fehlerhaft.x == 1 | Fehlerhaft.y == 1 | Fehlerhaft == 1 ) &
         ((year(as.Date(Fehlerhaft_Datum)) >= 2014 & year(as.Date(Fehlerhaft_Datum)) <= 2016) |
          (year(as.Date(Fehlerhaft_Datum.x)) >= 2014 & year(as.Date(Fehlerhaft_Datum.x)) <= 2016) |
          (year(as.Date(Fehlerhaft_Datum.y)) >= 2014 & year(as.Date(Fehlerhaft_Datum.y)) <= 2016))) 

glimpse(part_T01)
```
#2
```{r, message=FALSE, warning = FALSE, cache = TRUE}
txt <- readLines("Data/Einzelteil/Einzelteil/Einzelteil_T02.txt")
txt <- gsub("  ",",",txt, fixed = TRUE)
txt <- gsub("\t","\n",txt, fixed = TRUE)
part_T02 <- fread(text = txt, sep = ",", data.table = FALSE) %>% 
  filter((Fehlerhaft.x == 1 | Fehlerhaft.y == 1) &
         ((year(as.Date(Fehlerhaft_Datum.x)) >= 2014 & year(as.Date(Fehlerhaft_Datum.x)) <= 2016) |
          (year(as.Date(Fehlerhaft_Datum.y)) >= 2014 & year(as.Date(Fehlerhaft_Datum.y)) <= 2016))) 

glimpse(part_T02)
```
#3
```{r, message=FALSE, warning = FALSE, cache = TRUE}
txt <- readLines("Data/Einzelteil/Einzelteil/Einzelteil_T03.txt")
txt <- gsub("|",",",txt, fixed = TRUE)
txt <- gsub("\v","\n",txt, fixed = TRUE)
part_T03 <- fread(text = txt, sep = ",", data.table = FALSE) %>% 
  filter((Fehlerhaft== 1) &
         ((year(as.Date(Fehlerhaft_Datum)) >= 2014 & year(as.Date(Fehlerhaft_Datum)) <= 2016))) 

glimpse(part_T03)
```
#4
```{r, message=FALSE, warning = FALSE, cache = TRUE}
part_T04 <- fread("Data/Einzelteil/Einzelteil/Einzelteil_T04.csv", header = TRUE, data.table = FALSE) %>% 
  filter(Fehlerhaft == 1 &
         ((year(as.Date(Fehlerhaft_Datum)) >= 2014 & year(as.Date(Fehlerhaft_Datum)) <= 2016)))
glimpse(part_T04)
```
#5
```{r, message=FALSE, warning = FALSE, cache = TRUE}
part_T05 <- fread("Data/Einzelteil/Einzelteil/Einzelteil_T05.csv", header = TRUE, data.table = FALSE) %>% 
 filter((Fehlerhaft.x == 1 | Fehlerhaft.y == 1) &
         ((year(as.Date(Fehlerhaft_Datum.x)) >= 2014 & year(as.Date(Fehlerhaft_Datum.x)) <= 2016) |
          (year(as.Date(Fehlerhaft_Datum.y)) >= 2014 & year(as.Date(Fehlerhaft_Datum.y)) <= 2016))) 
glimpse(part_T05)
```
#6
```{r, message=FALSE, warning = FALSE, cache = TRUE}
part_T06 <- fread("Data/Einzelteil/Einzelteil/Einzelteil_T06.csv", header = TRUE, data.table = FALSE) %>% 
  filter(Fehlerhaft == 1 &
         ((year(as.Date(Fehlerhaft_Datum)) >= 2014 & year(as.Date(Fehlerhaft_Datum)) <= 2016)))
glimpse(part_T06)
```
#7
```{r, message=FALSE, warning = FALSE, cache = TRUE}
txt <- readLines("Einzelteil/Einzelteil/Einzelteil_T07.txt")
txt <- gsub("\"\t\"",",",txt)
txt <- gsub("\"\t",",",txt)
txt <- gsub("\t\"",",",txt)
txt <- gsub("\t",",",txt)
txt <- gsub("\"\"","\n",txt)
txt <- gsub("\"","\n",txt)
part_T07 <- fread(text = txt, sep = ",", quote = "", data.table = FALSE) %>% 
  filter((Fehlerhaft == 1) &
         ((year(as.Date(Fehlerhaft_Datum)) >= 2014 & year(as.Date(Fehlerhaft_Datum)) <= 2016))) 

glimpse(part_T07)
```
#8
```{r, message=FALSE, warning = FALSE, cache = TRUE}
part_T08 <- fread("Einzelteil/Einzelteil/Einzelteil_T08.csv", header = TRUE, data.table = FALSE) %>% 
  filter(Fehlerhaft == 1 &
         ((year(as.Date(Fehlerhaft_Datum)) >= 2014 & year(as.Date(Fehlerhaft_Datum)) <= 2016)))
glimpse(part_T08)
```
#9
```{r, message=FALSE, warning = FALSE, cache = TRUE}
txt <- readLines("Einzelteil/Einzelteil/Einzelteil_T09.txt")
txt <- gsub('\\\\', ',', txt, fixed = TRUE)
txt <- gsub("\f", "\n", txt, fixed = TRUE)
part_T09 <- fread(text = txt, sep = ",", data.table = FALSE) %>% 
 filter((Fehlerhaft.x == 1 | Fehlerhaft.y == 1) &
         ((year(as.Date(Fehlerhaft_Datum.x)) >= 2014 & year(as.Date(Fehlerhaft_Datum.x)) <= 2016) |
          (year(as.Date(Fehlerhaft_Datum.y)) >= 2014 & year(as.Date(Fehlerhaft_Datum.y)) <= 2016))) 

glimpse(part_T09)
```

data_txt <- read.table("C:/R-Dateien/data.txt", sep="\t", header=TRUE, dec=","
```{r, message=FALSE, warning = FALSE, cache = TRUE}
txt <- read.table("Einzelteil/Einzelteil/Einzelteil_T09.txt")
part_T09 <- fread(text = txt, sep = ",", data.table = FALSE) %>% 
 filter((Fehlerhaft.x == 1 | Fehlerhaft.y == 1) &
         ((year(as.Date(Fehlerhaft_Datum.x)) >= 2014 & year(as.Date(Fehlerhaft_Datum.x)) <= 2016) |
          (year(as.Date(Fehlerhaft_Datum.y)) >= 2014 & year(as.Date(Fehlerhaft_Datum.y)) <= 2016))) 

glimpse(part_T09)
```
#10

```{r, message=FALSE, warning = FALSE, cache = TRUE}
part_T10 <- fread("Einzelteil/Einzelteil/Einzelteil_T10.csv", header = TRUE, data.table = FALSE) %>% 
  filter(Fehlerhaft == 1 &
         ((year(as.Date(Fehlerhaft_Datum)) >= 2014 & year(as.Date(Fehlerhaft_Datum)) <= 2016)))
glimpse(part_T10)
```
#11
```{r, message=FALSE, warning = FALSE, cache = TRUE}
txt <- readLines("Einzelteil/Einzelteil/Einzelteil_T11.txt")
txt <- gsub("\t", ",", txt, fixed = TRUE)
txt <- gsub("\f", "\n", txt, fixed = TRUE)
part_T11 <- fread(text = txt, sep = ",", data.table = FALSE) %>% 
  filter(Fehlerhaft == 1 & 
         year(as.Date(Fehlerhaft_Datum)) >= 2014 & 
         year(as.Date(Fehlerhaft_Datum)) <= 2016) 

glimpse(part_T11)
```
#12
```{r, message=FALSE, warning = FALSE, cache = TRUE}
part_T12 <- fread("Einzelteil/Einzelteil/Einzelteil_T12.csv", header = TRUE, data.table = FALSE) %>% 
  filter(Fehlerhaft == 1 &
         ((year(as.Date(Fehlerhaft_Datum)) >= 2014 & year(as.Date(Fehlerhaft_Datum)) <= 2016)))
glimpse(part_T12)
```
#13
```{r, message=FALSE, warning = FALSE, cache = TRUE}
part_T13 <- fread("Einzelteil/Einzelteil/Einzelteil_T13.csv", header = TRUE, data.table = FALSE) %>% 
  filter(Fehlerhaft == 1 &
         ((year(as.Date(Fehlerhaft_Datum)) >= 2014 & year(as.Date(Fehlerhaft_Datum)) <= 2016)))
glimpse(part_T13)
```
#14
```{r, message=FALSE, warning = FALSE, cache = TRUE}
part_T14 <- fread("Einzelteil/Einzelteil/Einzelteil_T14.csv", header = TRUE, data.table = FALSE) %>% 
  filter(Fehlerhaft == 1 &
         ((year(as.Date(Fehlerhaft_Datum)) >= 2014 & year(as.Date(Fehlerhaft_Datum)) <= 2016)))
glimpse(part_T14)
```
#15
```{r, message=FALSE, warning = FALSE, cache = TRUE}
part_T15 <- fread("Einzelteil/Einzelteil/Einzelteil_T15.csv", header = TRUE, data.table = FALSE) %>% 
 filter((Fehlerhaft.x == 1 | Fehlerhaft.y == 1) &
         ((year(as.Date(Fehlerhaft_Datum.x)) >= 2014 & year(as.Date(Fehlerhaft_Datum.x)) <= 2016) |
          (year(as.Date(Fehlerhaft_Datum.y)) >= 2014 & year(as.Date(Fehlerhaft_Datum.y)) <= 2016))) 
glimpse(part_T15)
```
#16
```{r, message=FALSE, warning = FALSE, cache = TRUE}
txt <- readLines("Einzelteil/Einzelteil/Einzelteil_T16.txt")
txt <- gsub(" | | ",",",txt, fixed = TRUE)
txt <- gsub(" ","\n",txt, fixed = TRUE)
part_T16 <- fread(text = txt, sep = ",", data.table = FALSE) %>% 
  filter((Fehlerhaft.x == 1 | Fehlerhaft.y == 1 | Fehlerhaft == 1 ) &
         ((year(as.Date(Fehlerhaft_Datum)) >= 2014 & year(as.Date(Fehlerhaft_Datum)) <= 2016) |
          (year(as.Date(Fehlerhaft_Datum.x)) >= 2014 & year(as.Date(Fehlerhaft_Datum.x)) <= 2016) |
          (year(as.Date(Fehlerhaft_Datum.y)) >= 2014 & year(as.Date(Fehlerhaft_Datum.y)) <= 2016))) 

glimpse(part_T16)
```
#17
```{r, message=FALSE, warning = FALSE, cache = TRUE}
part_T17 <- fread("Einzelteil/Einzelteil/Einzelteil_T17.csv", header = TRUE, data.table = FALSE) %>% 
  filter((Fehlerhaft.x == 1 | Fehlerhaft.y == 1 | Fehlerhaft == 1 ) &
         ((year(as.Date(Fehlerhaft_Datum)) >= 2014 & year(as.Date(Fehlerhaft_Datum)) <= 2016) |
          (year(as.Date(Fehlerhaft_Datum.x)) >= 2014 & year(as.Date(Fehlerhaft_Datum.x)) <= 2016) |
          (year(as.Date(Fehlerhaft_Datum.y)) >= 2014 & year(as.Date(Fehlerhaft_Datum.y)) <= 2016))) 

glimpse(part_T17)
```
#18
```{r, message=FALSE, warning = FALSE, cache = TRUE}
part_T18 <- fread("Einzelteil/Einzelteil/Einzelteil_T18.csv", header = TRUE, data.table = FALSE) %>% 
  filter(Fehlerhaft == 1 &
         ((year(as.Date(Fehlerhaft_Datum)) >= 2014 & year(as.Date(Fehlerhaft_Datum)) <= 2016)))
glimpse(part_T18)
```
#19
```{r, message=FALSE, warning = FALSE, cache = TRUE}
part_T19 <- fread("Einzelteil/Einzelteil/Einzelteil_T19.csv", header = TRUE, data.table = FALSE) %>% 
  filter(Fehlerhaft == 1 &
         ((year(as.Date(Fehlerhaft_Datum)) >= 2014 & year(as.Date(Fehlerhaft_Datum)) <= 2016)))
glimpse(part_T19)
```
#20
```{r, message=FALSE, warning = FALSE, cache = TRUE}
txt <- readLines("Einzelteil/Einzelteil/Einzelteil_T20.txt")
txt <- gsub(" | | ",",",txt, fixed = TRUE)
txt <- gsub(" ","\n",txt, fixed = TRUE)
part_T20 <- fread(text = txt, sep = ",", data.table = FALSE) %>% 
    filter(Fehlerhaft == 1 &
         ((year(as.Date(Fehlerhaft_Datum)) >= 2014 & year(as.Date(Fehlerhaft_Datum)) <= 2016)))
glimpse(part_T20)
```
#21
```{r, message=FALSE, warning = FALSE, cache = TRUE}
part_T21 <- fread("Einzelteil/Einzelteil/Einzelteil_T21.csv", header = TRUE, data.table = FALSE) %>% 
  filter(Fehlerhaft == 1 &
         ((year(as.Date(Fehlerhaft_Datum)) >= 2014 & year(as.Date(Fehlerhaft_Datum)) <= 2016)))
glimpse(part_T21)
```
#22
```{r, message=FALSE, warning = FALSE, cache = TRUE}
txt <- readLines("Einzelteil/Einzelteil/Einzelteil_T22.txt")
txt <- gsub("\"\t\"",",",txt)
txt <- gsub("\"\t",",",txt)
txt <- gsub("\t\"",",",txt)
txt <- gsub("\t",",",txt)
txt <- gsub("\"\"","\n",txt)
txt <- gsub("\"","\n",txt)
part_T22 <- fread(text = txt, sep = ",", data.table = FALSE) %>% 
 filter((Fehlerhaft.x == 1 | Fehlerhaft.y == 1) &
         ((year(as.Date(Fehlerhaft_Datum.x)) >= 2014 & year(as.Date(Fehlerhaft_Datum.x)) <= 2016) |
          (year(as.Date(Fehlerhaft_Datum.y)) >= 2014 & year(as.Date(Fehlerhaft_Datum.y)) <= 2016))) 

glimpse(part_T22)
```
#23
```{r, message=FALSE, warning = FALSE, cache = TRUE}
part_T23 <- fread("Einzelteil/Einzelteil/Einzelteil_T23.csv", header = TRUE, data.table = FALSE) %>% 
 filter((Fehlerhaft.x == 1 | Fehlerhaft.y == 1) &
         ((year(as.Date(Fehlerhaft_Datum.x)) >= 2014 & year(as.Date(Fehlerhaft_Datum.x)) <= 2016) |
          (year(as.Date(Fehlerhaft_Datum.y)) >= 2014 & year(as.Date(Fehlerhaft_Datum.y)) <= 2016))) 
glimpse(part_T23)
```
#24
```{r, message=FALSE, warning = FALSE, cache = TRUE}
txt <- readLines("Einzelteil/Einzelteil/Einzelteil_T24.txt")
txt <- gsub("  ",",",txt, fixed = TRUE)
txt <- gsub("\f","\n",txt, fixed = TRUE)
part_T24 <- fread(text = txt, sep = ",", data.table = FALSE) %>% 
 filter((Fehlerhaft.x == 1 | Fehlerhaft.y == 1) &
         ((year(as.Date(Fehlerhaft_Datum.x)) >= 2014 & year(as.Date(Fehlerhaft_Datum.x)) <= 2016) |
          (year(as.Date(Fehlerhaft_Datum.y)) >= 2014 & year(as.Date(Fehlerhaft_Datum.y)) <= 2016))) 

glimpse(part_T24)
```
#25
```{r, message=FALSE, warning = FALSE, cache = TRUE}
part_T25 <- fread("Einzelteil/Einzelteil/Einzelteil_T25.csv", header = TRUE, data.table = FALSE) %>% 
  filter(Fehlerhaft == 1 &
         ((year(as.Date(Fehlerhaft_Datum)) >= 2014 & year(as.Date(Fehlerhaft_Datum)) <= 2016)))
glimpse(part_T25)
```
#26
```{r, message=FALSE, warning = FALSE, cache = TRUE}
part_T26 <- fread("Einzelteil/Einzelteil/Einzelteil_T26.csv", header = TRUE, data.table = FALSE) %>% 
  filter(Fehlerhaft == 1 &
         ((year(as.Date(Fehlerhaft_Datum)) >= 2014 & year(as.Date(Fehlerhaft_Datum)) <= 2016)))
glimpse(part_T26)
```
#27
```{r, message=FALSE, warning = FALSE, cache = TRUE}
txt <- readLines("Einzelteil/Einzelteil/Einzelteil_T27.txt")
txt <- gsub(" | | ",",",txt, fixed = TRUE)
txt <- gsub(" ","\n",txt, fixed = TRUE)
part_T27 <- fread(text = txt, sep = ",", data.table = FALSE) %>% 
  filter(Fehlerhaft == 1 &
         ((year(as.Date(Fehlerhaft_Datum)) >= 2014 & year(as.Date(Fehlerhaft_Datum)) <= 2016)))

glimpse(part_T27)
```
#30

```{r, message=FALSE, warning = FALSE, cache = TRUE}
part_T30 <- fread("Einzelteil/Einzelteil/Einzelteil_T30.csv", header = TRUE, data.table = FALSE) %>% 
   filter((Fehlerhaft.x == 1 | Fehlerhaft.y == 1 | Fehlerhaft == 1 ) &
         ((year(as.Date(Fehlerhaft_Datum)) >= 2014 & year(as.Date(Fehlerhaft_Datum)) <= 2016) |
          (year(as.Date(Fehlerhaft_Datum.x)) >= 2014 & year(as.Date(Fehlerhaft_Datum.x)) <= 2016) |
          (year(as.Date(Fehlerhaft_Datum.y)) >= 2014 & year(as.Date(Fehlerhaft_Datum.y)) <= 2016))) 

glimpse(part_T30)
```
#31
```{r, message=FALSE, warning = FALSE, cache = TRUE}
txt <- readLines("Einzelteil/Einzelteil/Einzelteil_T31.txt")
txt <- gsub("  ",",",txt, fixed = TRUE)
txt <- gsub("\b","\n",txt, fixed = TRUE)
part_T31 <- fread(text = txt, sep = ",", data.table = FALSE) %>% 
  filter(Fehlerhaft == 1 &
         ((year(as.Date(Fehlerhaft_Datum)) >= 2014 & year(as.Date(Fehlerhaft_Datum)) <= 2016)))

glimpse(part_T31)
```
#32
```{r, message=FALSE, warning = FALSE, cache = TRUE}
part_T32 <- fread("Einzelteil/Einzelteil/Einzelteil_T32.csv", header = TRUE, data.table = FALSE) %>% 
 filter((Fehlerhaft.x == 1 | Fehlerhaft.y == 1) &
         ((year(as.Date(Fehlerhaft_Datum.x)) >= 2014 & year(as.Date(Fehlerhaft_Datum.x)) <= 2016) |
          (year(as.Date(Fehlerhaft_Datum.y)) >= 2014 & year(as.Date(Fehlerhaft_Datum.y)) <= 2016))) 
glimpse(part_T32)
```
#33
```{r, message=FALSE, warning = FALSE, cache = TRUE}
part_T33 <- fread("Einzelteil/Einzelteil/Einzelteil_T33.csv", header = TRUE, data.table = FALSE) %>% 
  filter(Fehlerhaft == 1 &
         ((year(as.Date(Fehlerhaft_Datum)) >= 2014 & year(as.Date(Fehlerhaft_Datum)) <= 2016)))
glimpse(part_T33)
```
#34
```{r, message=FALSE, warning = FALSE, cache = TRUE}
txt <- readLines("Einzelteil/Einzelteil/Einzelteil_T34.txt")
txt <- gsub(" | | ",",",txt, fixed = TRUE)
txt <- gsub(" ","\n",txt, fixed = TRUE)
part_T34 <- fread(text = txt, sep = ",", data.table = FALSE) %>% 
  filter(Fehlerhaft == 1 &
         ((year(as.Date(Fehlerhaft_Datum)) >= 2014 & year(as.Date(Fehlerhaft_Datum)) <= 2016)))

glimpse(part_T34)
```
#35
```{r, message=FALSE, warning = FALSE, cache = TRUE}
txt <- readLines("Einzelteil/Einzelteil/Einzelteil_T35.txt")
txt <- gsub("\"", "", txt, fixed = TRUE)  # Entfernen Sie doppelte Anführungszeichen
txt <- gsub("\\\\", ",", txt, fixed = TRUE)  # Ersetzen Sie "\\"" durch Kommas
txt <- gsub("\v", "\n", txt, fixed = TRUE)  # Ersetzen Sie vertikale Tabulatoren durch Zeilenumbrüche
part_T35 <- fread(text = txt, sep = ",", data.table = FALSE)
 filter((Fehlerhaft.x == 1 | Fehlerhaft.y == 1) &
         ((year(as.Date(Fehlerhaft_Datum.x)) >= 2014 & year(as.Date(Fehlerhaft_Datum.x)) <= 2016) |
          (year(as.Date(Fehlerhaft_Datum.y)) >= 2014 & year(as.Date(Fehlerhaft_Datum.y)) <= 2016))) 

glimpse(part_T35)
```
#36
```{r, message=FALSE, warning = FALSE, cache = TRUE}
txt <- readLines("Einzelteil/Einzelteil/Einzelteil_T36.txt")
txt <- gsub("  ",",",txt, fixed = TRUE)
txt <- gsub("\t","\n",txt, fixed = TRUE)
part_T36 <- fread(text = txt, sep = ",", data.table = FALSE) %>% 
  filter(Fehlerhaft == 1 &
         ((year(as.Date(Fehlerhaft_Datum)) >= 2014 & year(as.Date(Fehlerhaft_Datum)) <= 2016)))
glimpse(part_T36)
```
#37
```{r, message=FALSE, warning = FALSE, cache = TRUE}
part_T37 <- fread("Einzelteil/Einzelteil/Einzelteil_T37.csv", header = TRUE, data.table = FALSE) %>% 
  filter(Fehlerhaft == 1 &
         ((year(as.Date(Fehlerhaft_Datum)) >= 2014 & year(as.Date(Fehlerhaft_Datum)) <= 2016)))
glimpse(part_T37)
```
#38
```{r, message=FALSE, warning = FALSE, cache = TRUE}
part_T38 <- fread("Einzelteil/Einzelteil/Einzelteil_T38.csv", header = TRUE, data.table = FALSE) %>% 
 filter((Fehlerhaft.x == 1 | Fehlerhaft.y == 1) &
         ((year(as.Date(Fehlerhaft_Datum.x)) >= 2014 & year(as.Date(Fehlerhaft_Datum.x)) <= 2016) |
          (year(as.Date(Fehlerhaft_Datum.y)) >= 2014 & year(as.Date(Fehlerhaft_Datum.y)) <= 2016))) 
glimpse(part_T38)
```
#39
```{r, message=FALSE, warning = FALSE, cache = TRUE}
txt <- readLines("Einzelteil/Einzelteil/Einzelteil_T39.txt")
txt <- gsub("\\\\", ",", txt, fixed = TRUE)
txt <- gsub("\v", "\n", txt, fixed = TRUE)
part_T39 <- fread(text = txt, sep = ",", data.table = FALSE) %>% 
  filter((Fehlerhaft.x == 1 | Fehlerhaft.y == 1) &
         ((year(as.Date(Fehlerhaft_Datum.x)) >= 2014 & year(as.Date(Fehlerhaft_Datum.x)) <= 2016) |
          (year(as.Date(Fehlerhaft_Datum.y)) >= 2014 & year(as.Date(Fehlerhaft_Datum.y)) <= 2016)))

glimpse(part_T39)
```

#40
```{r, message=FALSE, warning = FALSE, cache = TRUE}
part_T40 <- fread("Einzelteil/Einzelteil/Einzelteil_T40.csv", header = TRUE, data.table = FALSE) %>% 
  filter(Fehlerhaft == 1 &
         ((year(as.Date(Fehlerhaft_Datum)) >= 2014 & year(as.Date(Fehlerhaft_Datum)) <= 2016)))
glimpse(part_T40)
```











